### 2018-05-29 Physics Notes/Paper 2/Paper 2.tex
Physics Paper 2 Notes

\end{document}

>>>>

$$\frac{GM}{r^2}=\frac{v^2}{r}\quad \therefore v^2=\frac{GM}{r}$$
$$KE=\frac{1}{2}m\frac{GM}{r}$$
$$GPE=mV \quad	V=-\frac{GM}{r} \quad \therefore E_p=-\frac{GMm}{r}$$
$$E_T=E_K+E_P=\frac{GMm}{2r}+-\frac{GMm}{r}=-\frac{GMm}{2r}$$
\paragraph{Synchronous orbits}
$ $\\
\textbf{Geosynchronous orbit} - Time period of 24h, will be seen at the same place at the same time every day\\ 
\textbf{Geostationary orbit} - Time period of 24h, but in the plane of the equator and travelling the same direction as the earth, appears stationary to an observer on the ground\\
The height at which these satellites must be is determined by Kepler's law
\subsection{Electric fields}
\subsubsection{Coulomb's law}
This is the first equation under electric fields on the data sheet, it describes the force between two point charges in a vacuum\\
\textbf{Permittivity of free space} - The charge per unit area in coulombs per square metre on oppositely charged plates when the electric field strength between the plates is one volt per metre\\
The difference between the permittivity of free space and the permittivity of air is so insignificant air can be treated as a vacuum.\\
\textbf{Electric field strength} - At a point in an electric field, the force per unit charge on a small positively charged object in that field
\includegraphics[width=12cm]{field_lines.png} 

\paragraph{Derive $Fd=Q\Delta V$}
$$F=EQ \quad E=\frac{V}{d} \quad\therefore F=\frac{QV}{d} \quad\therefore Fd=QV$$
\paragraph{Particle in a uniform electric field}
\begin{center}
\includegraphics[width=8cm]{particle.jpg}
\end{center}
\end{document}
